The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-23 ms.Rmd
Update Feng_Papes workflow with new modules.

```{r, eval=FALSE}
Feng_Papes <- workflow(
    occurrence = SpOcc('Dasypus novemcinctus',
                       extent = c(-130, -20, -60, 60)),
    covariate = Bioclim(extent = c(-130, -20, -60, 60),
                        layers = c(1:4, 6, 9, 10, 12, 15)),
    process = Chain(TidyGBIF, # some sort of data cleaning?
                    BufferBackground, # background w/in 2 degrees of occurrences
                    MESSMask),  # mask out areas beyond extremes in train data
    model = MaxEnt,
    output = PrintMap)  # They plotted at 5% omission error level
```

>>>>

```{r, eval=FALSE}
Feng_Papes <- workflow(occurrence = SpOcc('Dasypus novemcinctus',
                                          extent = c(-130, -20, -60, 60)),
                        covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                            layers = c(1:4, 6, 9, 10, 12, 15)),
                          process = Chain(Clean, # Remove rows w/ impossible, unlikely or missing lat lon.
                                          Background(n = 1000, bias = 200), #background w/in 200km of occurrences
                                          # MESSMask),  # Still to be implemented. mask out areas beyond extremes in train data
                                          Crossvalidate(k = 5)),
                            model = MaxEnt,
                           output = Chain(PerformanceMeasures, PrintMap))

```
